### 2023-11-14 main.tex
^^

@@

 The basis element $ (E_{ab})_{a,b\in\{1,\ldots,N\}}$ of $gl(N)$ can also be thought as proper compositions of the rising, and lowering operators of th Heisenberg Lie algebra
  \begin{equation}\label{creationOperators}
	\oad_{a}|n_{1},\ldots,n_{a},\ldots,n_{N}\rangle = |n_{1},\ldots,n_{a}+1,\ldots,n_{N}\rangle\\
	\oa_{a}|n_{1},\ldots,n_{a},\ldots,n_{N}\rangle =n_{a}|n_{1},\ldots,n_{a}-1,\ldots,n_{N}\rangle
with commutaion relations
	[\oad_{a},\oa_{b}]=-\mathbbm{1}\,\delta_{ab}
Therefore, we have that 
		E_{ab}=\oad_{a}\oa_{b}\qquad \forall a,b=1,\ldots N
fulfil the action on the basis vector \eqref{actionE} and the commutation relation \eqref{eq:comgl} }
\section{Exact steady state of $H$}\label{appB}
where for every $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$
		\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
where the last expectation is taken with respect to the $\mu^{\text{NESS}}$ of the process $\bm{\sigma}$ and is given in \eqref{exactCorrelations}.
		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})
As a consequence, one cha interpret the $m$-point correlations computed in \eqref{exactCorrelations} as the steady state of a chain of length $m$ where the sites have coordinates $x_{1},\ldots,x_{m}$ and they are occupied by $a_{1},\ldots,a_{m}$. 
	=&\sum_{\bm{\sigma}\in \Omega}\Psi^{'}(\bm{\sigma})\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},\sigma_{x}}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_{x},i_{x}}\right)\nonumber\\
	=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
In the last equality we exploited the fact that considering any $\tau_{x}\in \{1,\ldots,N\}$ and $i_{x}\in \{1,\ldots,N-1\}$, and considering a configuration $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$ such that 
		\sigma_{x}=i_{x}\qquad &\text{if}\quad x\in \{q_{1},\ldots,q_{b}\}\\
		\sigma_{x}=\tau_{x}\qquad &\text{if}\quad \text{otherwise}
we have that 
	 \Psi^{'}(\bm{\sigma})=\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
as showed in Section \ref{correlation-section}. 
	\begin{remark}[Proof of \eqref{SteadyState-coeff-implicit} using the conservation of probability]
		Equation \eqref{SteadyState-coeff-implicit} can be proved also using the conservation of probability in the non-equilibrium steady state. Consider a generic $\bm{\tau}\in \Omega$, then we have 
Introducing the summation over $b$, the coordinates $(q_{k})_{k\in {1,\ldots,b}}$ and the indices $i_{q_{k}}$ as in the previous proof and arguing as in Section \ref{correlation-section}, one find \eqref{SteadyState-coeff-implicit}. 
	\textbf{Proof}: we aim to show that 
		\sum_{\bm{\tau}\in \Omega}\Psi(\bm{\tau})=&\sum_{\bm{\tau}\in \Omega}\Psi^{'}(\bm{\tau})\nonumber\\+&\sum_{\bm{\tau}\in \Omega}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\=&1

>>>>

\subsection{Explicit steady state of $H$}\label{appB}
In this section we write an explicit formula for the non-equilibrium steady state of $H$ defined in \eqref{definition-SteadyStateH}. This formula is follows from the ground state $|\Psi^{'}\rangle$found in \eqref{ABS_1}.
	where, for every $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})\in \Omega$,
			\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots i_{q_{b}}=1}^{N-1}\mathfrak{M}(\bm{\tau},q_{1},\dots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})%\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
			\mathfrak{M}(\bm{\tau},q_{1},\ldots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})=&\sum_{t_{1}=0}^{1-\delta_{\tau_{1},N}+Q(1)}\ldots\sum_{t_{L}=0}^{1-\delta_{\tau_{L},N}+Q(L)}\left(\prod_{k=1}^{b}\alpha_{i_{q_{k}}}^{t_{q_{k}}}\beta_{i_{q_{k}}}^{1-t_{q_{k}}}\right)\left(\prod_{x=1}^{L}\alpha_{\tau_{x}}^{t_{x}}\beta_{\tau_{x}}^{(1-t_{x}-\delta_{\tau_{x},N})}\right)\\&
			\;\;\;\;\;\;\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{L}=t_{L}}^{1}f(c_{1},\ldots,c_{L})\prod_{x=1}^{L}(-1)^{c_{x}-t_{x}}g_{x}(x,c_{x},\ldots,c_{L})
	%	&\mathfrak{M}(\bm{\tau},q_{1},\ldots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})=\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}+Q(1)}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}+Q(L)}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)\\
	%	&\left(\prod_{k=1}^{b}\left(\alpha_{i_{q_{k}}}-\beta_{i_{q_{k}}}\right)^{1-c_{q_{k}}}\beta_{i_{q_{k}}}^{c_{q_{k}}}\right)\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}\right)
		Q(x)=\sum_{k=1}^{b}\delta_{x,q_{k}}
and $f(c_{1},\ldots,c_{L})$ and $g_{x}(x,c_{x},\ldots,c_{L})$ defined in \eqref{powerCoeffNOspec} and \eqref{powerCoeffSpecies} respectively. 
%	Q(x)=1-\sum_{k=1}^{b}\delta_{x,q_{k}}
%	Moreover, $\Psi(\bm{\tau})$ are interpreted as the probabilities in the steady state of having a configuration $\bm{\tau}$, i.e.
%%	\end{equation}
		\Psi(\bm{\tau})=\Psi^{'}(\bm{\tau})=\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]\dt
%where the expectation is take with respect to the $\mu_{\text{NESS}}$ of the process $\bm{\sigma}=(\sigma_{1},\ldots,\sigma_{L})$. 
	%As a consequence, one can interpret the $m$-point correlations computed in \eqref{exactCorrelations} as the steady state of a chain of length $m$ where the sites have coordinates $x_{1},\ldots,x_{m}$ and they are occupied by $a_{1},\ldots,a_{m}$. 
				=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\sum_{\bm{\sigma}\in \Omega}\Psi^{'}(\bm{\sigma})\left(\prod_{x=1\,:\,x\notin\{q_{1},\ldots,q_{b}\}}^{L}\delta_{\tau_{x},\sigma_{x}}\right)\left(\prod_{x\in \{q_{1},\ldots,q_{b}\}}\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\sigma_{x},i_{x}}\right)\nonumber\\
				=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathfrak{M}(\bm{\tau},q_{1},\ldots,q_{b},i_{q_{1}},\ldots,i_{q_{b}})
		In the last equality we have used equation \eqref{ABS_1}. 
			\begin{remark}[Non-equilibrium steady state using exact correlations]
			A formula for $|\Psi\rangle$ can be also obtain using the conservation of probability in the non-equilibrium steady state. Consider a generic $\bm{\tau}\in \Omega$, then we have 
				Introducing the summation over $b$, the coordinates $(q_{k})_{k\in {1,\ldots,b}}$ and the indices $i_{q_{k}}$ as in the previous proof and arguing as in Section \ref{correlation-section}, we have that 
				\Psi(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}},\ldots,i_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=i_{q_{k}}\}}\prod_{x=1\,:\,x\notin \{q_{1},\ldots,q_{k}\}}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
			where the expectation can be computed using \eqref{exactCorrelations}. 
			\textbf{Proof}: here we write  
				\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
			meaning that, for all $b\in \{0,\ldots,L\}$ and for all $1\leq q_{1}<\ldots<q_{b}\leq L$,
					\tau_{x}=i_{x}\qquad &\text{if}\quad x\in\{q_{1},\ldots,w_{b}\}\\
					\tau_{x}=\tau_{x}\qquad &\text{if}\quad \text{otherwise}
			We aim to show that 
				&\sum_{\bm{\tau}\in \Omega}\Psi(\bm{\tau})=\sum_{\bm{\tau}\in \Omega}\Psi^{'}(\bm{\tau})\nonumber\\+&\sum_{\bm{\tau}\in \Omega}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\=&1

@@

 The basis element $ (E_{ab})_{a,b\in\{1,\ldots,N\}}$ of $gl(N)$ can also be thought as proper compositions of the rising, and lowering operators of th Heisenberg Lie algebra
  \begin{equation}\label{creationOperators}
	\begin{cases}
	\oad_{a}|n_{1},\ldots,n_{a},\ldots,n_{N}\rangle = |n_{1},\ldots,n_{a}+1,\ldots,n_{N}\rangle\\
	\oa_{a}|n_{1},\ldots,n_{a},\ldots,n_{N}\rangle =n_{a}|n_{1},\ldots,n_{a}-1,\ldots,n_{N}\rangle
	\end{cases}
\end{equation}
with commutaion relations
\begin{equation}
	[\oad_{a},\oa_{b}]=-\mathbbm{1}\,\delta_{ab}
\end{equation}
Therefore, we have that 
\begin{equation}
		E_{ab}=\oad_{a}\oa_{b}\qquad \forall a,b=1,\ldots N
\end{equation} 
fulfil the action on the basis vector \eqref{actionE} and the commutation relation \eqref{eq:comgl} }
\end{comment}
